Empirical normative theories

### 2020-06-25 simple.tex
Rm unused proof and prop about attack-exists

\begin{theorem}
	An empirical theory is convincing iff it has no falsification instances.
\end{theorem}
\begin{proof}
	For all $i \in I, \phi \in {\gleadsto}(\allargs)$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.

	For all $i \in I, \phi \in {\gleadsto}(\allargs)$, the following equivalences hold. $\forall \ar \in \gargs[i, \phi]$, $\ar$ $i$-defends $\phi$ iff $\forall \ar \in \gargs[i, \phi], \hist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset\right]$, $\hist \ileadstosti \phi$ iff $\forall \hist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset\right]$, $(i, \phi, \hist)$ is not a falsification instance.
\end{proof}

\begin{proposition}
	$\forall i \in I, \phi \in \Phi, \ar_0 \in \allargs$:
\begin{equation}
	\label{eq:st-in-terms-of-e}
	\ar_0 \nileadstosti \phi ⇔ [\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatsi \ar_0].
\end{equation}
\end{proposition}
\begin{proof}
	By definition of ${\ileadstosti}$, $\ar_0 \ileadstosti \phi ⇔ \forall \hist \in \allhist \suchthat \ar_0 \in \histend: \hist \ileadstosti \phi$. 
Equivalently, $\ar_0 \ileadstosti \phi ⇔ \forall \hist \in \allhist \suchthat [\exists \ar_1 \in \allargs \suchthat \set{\ar_1, \ar_0} \subseteq \histend]: \hist \ileadstosti \phi$. 
Still equivalently, $\ar_0 \nileadstosti \phi ⇔ \exists \hist \in \allhist \suchthat [\exists \ar_1 \in \allargs \suchthat \set{\ar_1, \ar_0} \subseteq \histend] \land \hist \nileadstosti \phi$. 
It can also be written $\ar_0 \nileadstosti \phi ⇔ \exists \hist \in \allhist, \ar_1 \in \allargs \suchthat \set{\ar_1, \ar_0} \subseteq \histend \land \hist \nileadstosti \phi$. By definition of ${\ibeatsi}$, this is the proposition to be proven.
\end{proof}

>>>>

\begin{theorem}
	An empirical theory is convincing iff it has no falsification instances.
\end{theorem}
\begin{proof}
	For all $i \in I, \phi \in {\gleadsto}(\allargs)$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
\end{proof}
